### 2023-01-11 definitions.tex
Searching for counter-examples

\"Ozkan goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). The characterization is used to show that Petri nets are $\post^*$ -effective. It is well-known that Petri nets constitute WSTS with storng monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS0}).
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the WSTS framework.

@@

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, on ewould be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}

@@

\begin{proof}
leur algorithme termine mais pas correct car l'intersection de post et J car alors le lemmme xxxx est faux (contre-exemple)
 \textcolor{red}{à faire Mathieu}
\end{proof}

>>>>

\"Ozkan goes on to prove that for finite-branching WSTS with strong monotonicity, a basis of $\uparrow \post^*(s)$ is computable for every given state $s$ iff the downward-closed problem is decidable, i.e. given a state $s$ of a WSTS
% in the regarded class 
with strong monotonicity 
and a decidable downward-closed set $J$, it can be decided whether $\exists s' \in J ~ s \to^* s'$ (Proposition~1 in \cite{DBLP:conf/gg/Ozkan22}). The characterization is used to show that Petri nets are $\post^*$ -effective. It is well-known that Petri nets constitute WSTS with storng monotonicity (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}).
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the WSTS framework.

@@

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow \post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, one would be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}

@@

\begin{proof}
leur algorithme termine mais pas correct car l'intersection de post et J car alors le lemmme xxxx est faux (contre-exemple)
 \textcolor{red}{à faire Mathieu}

\mathieu{En train de chercher un contre exemple pour le Lemme~\ref{Lemma intersection}.}

\end{proof}
